Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
fit weibull to seed data and subsamps

>>>>

Next steps.
Fit a weibull distribution to the raw seed dispersal data, probably subsample.
Provide summary stats for the dispersal and dispersion measures.

```{r}
# s.df <- df %>% drop_na(s.id)

s.df <- df %>% drop_na(s.id) %>% 
  sample_n(., 50)

library(fitdistrplus)

g <- fitdist(s.df$disp, distr = "weibull")
summary(g)
plot(g)

# library(MASS)
# fitdistr(s.df$disp, densfun = "weibull")
```
